\textbf{INSERT TITLE HERE}

### 2013-11-16 LaTeX/paper.tex
Added function for Z_AB(t) and added variables

\subsection{Part 1?}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.

>>>>

\subsection{Part 1?}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.
\begin{description}
    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
    \item[$v$] required ambulance response time
    \item[$T_{AB}$] travel time from A to B, given
    \item[$T_{BA}$] travel time from B to A, given
    \item[$P_B$] total population of B
    \item[$T_{A^+}$] travel time inside of A traveling away from B
    \item[$T_{A^-}$] travel time inside of A traveling toward B
    \item[$T_{B^+}$] travel time inside of B traveling away from A
    \item[$T_{B^-}$] travel time inside of B traveling toward A
    \item[$a, b$] width of A and B respectively
    \item[$g$] width of the gap between A and B
\end{description}

%TODO: Graphical representation of origin and setup
The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B * \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
